\documentclass[10pt,a4paper]{moderncv}
\moderncvtheme[blue]{classic}      
\usepackage[scale=0.8]{geometry}
\usepackage{color}
\definecolor{myblue}{RGB}{55,115,179}
\recomputelengths

\firstname{\color{gray}\huge{\textbf{Sebastian}} }
\familyname{\color{black}\huge{\textbf{Bustamante Jaramillo}}}
\title{\large{Publications and events}}
\nopagenumbers{}

\AfterPreamble{\hypersetup{
  pdfauthor={Sebastian Bustamante},
  pdftitle={Publications of Sebastian Bustamante},
  urlcolor=blue,
}}



%**************************************************************************************************

\begin{document}

\vspace{1.0cm}
\maketitle
	
%==================================================================================================
\section{\textsc{Publications}}
%==================================================================================================

%--------------------------------------------------------------------------------------------------
\subsection{\textsc{1st author}}
%--------------------------------------------------------------------------------------------------

\cvitem{\small\textbf{2017}}
	{\textbf{Merger-induced metallicity dilution in cosmological galaxy formation simulations.}}
\cvitem{}
	{S. Bustamante, M. Sparre, V. Springel, R.J.J Grand.}
\cvitem{}	
	{\textit{Submitted to MNRAS.}}

\vspace{0.1cm}
\cvitem{\small\textbf{2015}}
	{\textbf{Tensor anisotropy as a tracer of cosmic voids.}}
\cvitem{}
	{S. Bustamante, J.E. Forero-Romero.}
\cvitem{}
	{MNRAS 453 1 497, 2015.}
\cvitem{}
	{\textbf{ADS:} \url{adsabs.harvard.edu/abs/2015MNRAS.453..497B}}
\vspace{0.1cm}

%--------------------------------------------------------------------------------------------------
\subsection{\textsc{2nd author}}
%--------------------------------------------------------------------------------------------------	

\cvitem{\small\textbf{2017}}
	{\textbf{Origin of chemically distinct discs in the Auriga cosmological simulations.}}
\cvitem{}
	{R.J.J. Grand, S. Bustamante, F.A. Gómez, D. Kawata, F. Marinacci, R. Pakmor, H-W. Rix., C.M. Simpson, M. Sparre, V. Springel.}
\cvitem{}
	{\textit{Accepted for publication in MNRAS}} 
\cvitem{}
	{\textbf{ADS:} \url{adsabs.harvard.edu/abs/2017arXiv170807834G}}
\vspace{0.1cm}

\cvitem{\small\textbf{2017}}
	{\textbf{Geomagnetic properties of Proxima Centauri b analogues.}}
\cvitem{}
	{J.I. Zuluaga, S. Bustamante.}
\cvitem{}
	{\textit{Submitted to Planetary and Space Science}, Arxiv 1609.00707.} 
\cvitem{}
	{\textbf{ADS:} \url{adsabs.harvard.edu/abs/2016arXiv160900707Z}}
	
\vspace{0.1cm}
\cvitem{\small\textbf{2013}}
	{\textbf{The influence of thermal evolution in the magnetic protection of terrestrial planets.}} 
\cvitem{}
	{J.I. Zuluaga, S. Bustamante, P.A Cuartas, J.H. Hoyos.} 
\cvitem{}
	{ApJ 770 23, 2013.} 
\cvitem{}
	{\textbf{ADS:} \url{adsabs.harvard.edu/abs/2013ApJ...770...23Z}}
\vspace{0.1cm}

%--------------------------------------------------------------------------------------------------
\subsection{\textsc{nth author}}
%--------------------------------------------------------------------------------------------------	

\cvitem{\small\textbf{2017}}
	{\textbf{Lessons from the Auriga discs: the hunt for the Milky Way's ex situ disc is not yet over.}}
\cvitem{}
	{F.A. Gómez, R.J.J. Grand, A. Monachesi, S.D.M. White, \textbf{S. Bustamante}, F. Marinacci, R. Pakmor, C.M. Simpson, V. Springel, D.J.R. Campbell, C.S. Frenk, A. Jenkins.} 
\cvitem{}
	{MNRAS 472 3 3772, 2017.}
\cvitem{}
	{\textbf{ADS:} \url{http://adsabs.harvard.edu/abs/2017MNRAS.472.3722G}}
\vspace{0.1cm}


\cvitem{\small\textbf{2013}}
	{\textbf{The kinematics of the Local Group in a cosmological context.}}, 
\cvitem{}
	{J.E. Forero-Romero, Y. Hoffman, \textbf{S. Bustamante}, S. Gottloeber, G. Yepes.}
\cvitem{}
	{ApJL 767 L5, 2013.} 
\cvitem{}
	{\textbf{ADS:} \url{adsabs.harvard.edu/abs/2013ApJ...767L...5F}}
\vspace{0.1cm}

%--------------------------------------------------------------------------------------------------
\subsection{\textsc{In preparation}}
%--------------------------------------------------------------------------------------------------	
\cvitem{}
	{\textbf{Spin evolution of supermassive black holes in a cosmological context.}}
\cvitem{}
	{S. Bustamante, V. Springel.}
\vspace{0.1cm}
	
%==================================================================================================
\section{\textsc{Talks}}
%==================================================================================================


\cvitem{\small\textbf{2017}}
	{\textbf{Spin evolution of supermassive black holes in a cosmological context.}}
\cvitem{}
	{CAASTRO Conference. From Black Hole to Environment, Canberra, Australia.}
\vspace{0.1cm}

\cvitem{\small\textbf{2017}}
	{\textbf{Merger-induced metallicity dilution in cosmological galaxy formation simulations.}}
\cvitem{}
	{Conference the Galaxy Ecosystem. Flow of Baryons through Galaxies, Garching, Germany.}
\vspace{0.1cm}

\cvitem{\small\textbf{2016}}
	{\textbf{Spin evolution of supermassive black holes.}}
\cvitem{}
	{Virgo Meeting, Durham, United Kingdom.}

\vspace{0.1cm}
\cvitem{\small\textbf{2015}}
	{\textbf{Tracing cosmic voids in cosmological simulations.}}
\cvitem{}
	{Potsdam Institute for Astrophysics (AIP), Potsdam, Germany.}

\vspace{0.1cm}
\cvitem{\small\textbf{2014}}
	{\textbf{The fractional anisotropy as a tracer of cosmic voids.}}
\cvitem{}
	{4th Colombian Congress of Astronomy and Astrophysics, Pasto, Colombia.}
	
\vspace{0.1cm}
\cvitem{\small\textbf{2012}}
	{\textbf{The place of the Local Group in the cosmic web.}}
\cvitem{}
	{3rd Colombian Congress of Astronomy and Astrophysics, Bucaramanga, Colombia.}

\vspace{0.1cm}
\cvitem{\small\textbf{2012}}
	{\textbf{Numerical modelling of the interior and thermal evolution of habitable planets.}}
\cvitem{}
	{2nd International Congress of Astrobiology, Medellín, Colombia.}
	
\vspace{0.1cm}
\cvitem{\small\textbf{2011}}
	{\textbf{Thermal evolution of rocky exoplanets.}}
\cvitem{}
	{3rd International Congress of Formation and Modelling in Basic Sciences, Medellín, Colombia.}
	
\vspace{0.1cm}
\cvitem{\small\textbf{2010}}
	{\textbf{PLYNET, Python Planetary Physics Package.}}
\cvitem{}
	{2nd Colombian Congress of Astronomy and Astrophysics, Bogotá, Colombia}
	
	
%==================================================================================================
\section{\textsc{Schools and Workshops}}
%==================================================================================================

\cvitem{\small\textbf{2017}}
	{\textbf{IMPRS Summer School on compact objects and gravitational waves.}}
\cvitem{}
	{Max Planck Institute for Astronomy, Heidelberg, Germany.}
\vspace{0.1cm}

\cvitem{\small\textbf{2017}}
	{\textbf{The IFT School on cosmology tools.}}
\cvitem{}
	{Universidad Autónoma de Madrid, Madrid, Spain.}
\vspace{0.1cm}

\cvitem{\small\textbf{2016}}
	{\textbf{IMPRS Summer School on astrostatistics.}}
\cvitem{}
	{Max Planck Institute for Astronomy, Heidelberg, Germany.}
	
\cvitem{\small\textbf{2014}}
	{\textbf{1st Andean School of Astronomy and Astrophysics (EAAA).} }
\cvitem{}
	{Quito, Ecuador.}


\end{document}
